---
title: "Latest Updates"
author: "L-ENA"
date: "2020-10-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

Latest published version: [placeholder]

This page contains the latest updates to this living review. We have screened and continued the work on this review, a status update and resources are given below.

### Screening status
Number of abstracts screened since the last publication: 0

Number of full texts screened since the last publication: 0

Number of papers included since the last publication: 0

Last updated: 02-11-2020 (PubMed, arXiv); 02-11-2020 (DBLP)

### PRISMA 2020 flow diagram

This is the PRISMA diagram for the first version of the living review.

```{r, echo=FALSE}
htmltools::includeHTML("figures/prisma.html")

```

The PRISMA diagrams were created using [Haddaway, NR. 2020. SRflowdiagram: flow charts for systematic reviews and maps. doi: 10.5281/zenodo.4134795](https://zenodo.org/record/4134795#.X67YUlCnxaQ)

### Latest figures

These figures represent pre-update, and therefore unpublished, content from the living review. 

```{r, echo=FALSE}
htmltools::includeHTML("figures/bar_System_architectures.html")
htmltools::includeHTML("figures/bar_App_or_user_interface_availability.html")
htmltools::includeHTML("figures/year_bar.html")
```





