---
title: "Latest Updates"
author: "Lena Schmidt"
date: "August 3th, 2021"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

Latest published version: [ Data extraction methods for systematic review (semi)automation: A living systematic review (version 1; peer review: 1 approved)](https://f1000research.com/articles/10-401)

This page contains the latest updates to this living review. We have screened and continued the work on this review, a status update and resources are given below.

Current literature updates, extraction progress and duplicates are accessible by clicking on the relevant fields of the PRISMA2020 diagram.

### Screening status after publication of base-review

Latest references retrieved: Aug 2nd 2021 (PubMed, ArXiv, ACL, DBLP, EPPI-Reviewer Microsoft Academic)

Number of abstracts retrieved (post base-review): 5307



Number of abstracts screened: 402

Number of abstracts sent for full-text assessment: 13


Number of full-texts included: 0

Number of full-texts excluded: 0

### PRISMA 2020 flow diagram for the base review

This is the PRISMA diagram for the first update of this living review (work in progress, see base review for published results).

```{r, echo=FALSE}
htmltools::includeHTML("figures/new_prisma.html")

```

The PRISMA diagrams were created using [Haddaway, NR. 2020. SRflowdiagram: flow charts for systematic reviews and maps. doi: 10.5281/zenodo.4134795](https://zenodo.org/record/4134795#.X67YUlCnxaQ)

### Latest figures

These figures represent pre-update, and therefore unpublished, content from the living review. 

```{r, echo=FALSE}
htmltools::includeHTML("figures/bar_System_architectures.html")
htmltools::includeHTML("figures/bar_App_or_user_interface_availability.html")
htmltools::includeHTML("figures/year_bar.html")
```





